Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound

### 2019-03-05 ongoing/report/4_simulation.tex
Reformatting source

As of now, we have transformed the sparse-recovery problem of complex matrix \(H\) to complex vector \(h\), and finally to real vector \(\MC{R}(h)\).
But it is not the end.
In fact, Cand\`es and Tao's analysis in ``\(\ell_1\)-MAGIC'' transforms DS into a linear program (LP), but that does not directly applies
Actually they pointed out that complex DS may be cast into a second order cone program (SOCP), but (as they admit in the paper) they did not pursue the matter.
Since the proof is, for the present purpose, not entirely trivial, we include here for completeness of exposition.
Thus our proposed algorithm is not a corollary of the DS program outlines in ``\(\ell_1\)-MAGIC''.

@@

Since our setting is slightly different from ``\(\ell_1\)-MAGIC'', for completeness of exposition we write down derivation of the dual problem from the primal problem, as follows.
Recapitulate that, as we explained in the above, DS involves the calculation of \(\ell_1\)-1 norm.
This, for real vectors, can be transformed into a linear program (LP).
But in the complex case, that becomes a quadratic expression of the real and imaginary part of the vector, and is no longer equivalent to an LP.
Still, the comparison arising from primal-dual problem is not easily done in complex numbers, and we cast it into a real \(\ell_1\)-1 norm problem.
Afterwards we will further transform the SOCP to a primal-dual algorithm, which is a well-known technique for convex optimization problems.
The bound in the previous section is valid, since in the course of transformation, nothing is lost or weakened.

@@

\Result
{Definition}
{
For \(x \in \MB{V}(M)\), we say \(\MC{R}(x)\) is the real representation of \(x\), defined by
%
\Disp{
\MC{R}(x) \in \NC \MB{V}(2M) \NR
\MC{R}(x)(m) =
\NC \begin{cases}
\MF{Re}(\MC{R}(x)(m)), \NC m =2m' \NR[+]
\MF{Im}(\MC{R}(x)(m)), \NC m =2m'+1
\end{cases} \NR[+]
m' =\NC  1, \dots, M \NT
}
%
}

@@

\Result
{Definition}
{
For \(A \in \MB{M}_{\MB{C}} (M_1, M_2)\), we say \(\MC{R}(A)\) is the real representation of \(A\), defined by
%
\Disp{
A \in \NC \MB{V}_{\MB{R}} (2M_1, 2M_2) \NR
A (m_1,m_2) =
\NC \begin{cases}
\MF{Re}(A (m_1,m_2)), \NC m_1 =2m_1'-1,\; m_2 =2m_2'-1  \NR[+]
\MF{Im}(A (m_1,m_2)), \NC m_1 =2m_1',\; m_2 =2m_2'-1  \NR[+]
-\MF{Im}(A (m_1,m_2)), \NC m_1 =2m_1'-1,\; m_2 =2m_2'  \NR[+]
\MF{Re}(A (m_1,m_2)), \NC m_1 =2m_1',\; m_2 =2m_2'  \NR[+]
\end{cases} \NR[+]
m_1' = \NC 1, \dots, m_1 \NR
m_2' = \NC 1, \dots, m_2 \NT
}
%
}

@@

%
\Disp{
\V{\T{y}}
=\NC \MC{R}(y)
\in \MB{V}(N_h) \NR[+]
\V{\T{g}}
=\NC \MC{R}(g)
\in \MB{V}(N_h) \NR[+]
\M{\T{P}}
=\NC \MC{R}(\M{P})
\in \MB{M}_{\MB{C}} (2 N_y^2, 2 N_h^2)
}
%
such that
%
\Disp{
\V{\T{y}} =\M{\T{P}} \V{\T{g}} +\V{\T{z}}
}
%
where by construction
%
\Disp{
\V{\T{z}}
=\MC{R}(\V{z}) \in \MB{V}(N_y)
}
%

Finally, introduce these indicator matrices to identify the place where we want to take \(\ell_2\)-norm.

%
\Disp{
\M{I}_{n_y}^{(y)} \in \NC \MB{M}_{\MB{R}} (2N_y^2, 2N_y^2) \NR
\M{I}_{n_y}^{(y)}(n_y')
=\NC \begin{cases}
1, \NC n_y' =2n_y \NR[+]
1, \NC n_y' =2n_y +1 \NR[+]
0, \NC \RM{otherwise}
\end{cases} \NR[+]
\M{I}_{n_h}^{(h)} \in \NC \MB{M}_{\MB{R}} (2N_h^2, 2N_h^2) \NR
\M{I}_{n_h}^{(h)}(n_h')
=\NC \begin{cases}
1, \NC n_h' =2n_h \NR[+]
1, \NC n_h' =2n_h +1 \NR[+]
0, \NC \RM{otherwise}
\end{cases} \NR[+]
n_y =\NC 1, \dots, N_y \NR
n_h =\NC 1, \dots, N_h \NT
}
%

If we introduce vector \(\V{m}\) to denote the entrywise complex modulus, we see that Program () now take the form

\Result
{Program}
{
   Given are \(\T{\M{P}}, \T{\V{y}}, \gamma\).
Find \(\T{\V{g}}\) with
%
\Disp{
\min_{\T{\V{g}}, \V{m}} \quad
\NC \IP{ \V{1}, \V{m} } \NR
\RM{subject}\; \RM{to} \quad
\NC \begin{cases}
\| \M{I}_{n_h}^{(h)} \T{\V{g}} \|_2
\leq \IP{ \V{y}_{n_h}, \V{m} } \NR[+]
\| \M{I}_{n_y}^{(y)} \T{\M{P}}^\H ( \T{\M{P}} \T{\V{g}} -\T{\V{y}} ) \|_2
\leq \gamma  \NR[+]
\end{cases}
}
%
where \(\V{1}\) is the all-1 vector.
}

@@

It remains to convert primal-dual interior point algorithm to make the SOCP easier to calculate.
Of course it is not the only way to do this.
We mention, again, Boyd and Vandenberghe (2004), {\it Convex Optimization} chap.11 as a standard reference, and ``\(\ell_1\)-MAGIC'' (Cand\`es and J Romberg 2005) for discussion of application to DS.

To clarify notation and for complentess of exposition, we derive the dual problem here.
Start with the Lagrangian \(\MC{L}\), where we note we have to introduce one auxiliary vector and one auxiliary scalar for each \(\ell_2\)-norm constraint.

%
\Disp{
\NC \NC \MC{L}(\V{m}, \T{\V{g}}, \V{\mu}^{(h)}, \V{\mu}^{(y)}, \lambda^{(h)}, \lambda^{(y)}) \NR
\NC =\NC \IP{\V{1}, \V{m}}
+\sum_{n_h} \SB {\IP {\V {\mu}^{(h)}, \M {I}_{n_h}^{(h)} \T {\M{g}}} -\lambda^{(h)} \IP {\V{y}_{n_h}, \V{m}}} \NR
\NC \quad \NC  +\sum_{n_y} \SB{ \IP{ \V{\mu}^{(h)}, \M{I}_{n_y}^{(y)} \T{\M{P}}^\H ( \T{\M{P}} \T{\V{g}} -\T{\V{y}} ) } -\lambda^{(h)} \gamma} \NR[+]
}
%

>>>>

As of now, we have transformed the sparse-recovery problem of complex matrix \m {H} to complex vector \m {h}, and finally to real vector \m {\MC {R} (h)}.
But it is not the end.
In fact, Cand\`es and Tao's analysis in ``\m {\ell_1}-MAGIC'' transforms DS into a linear program (LP), but that does not directly applies
Actually they pointed out that complex DS may be cast into a second order cone program (SOCP), but (as they admit in the paper) they did not pursue the matter.
Since the proof is, for the present purpose, not entirely trivial, we include here for completeness of exposition.
Thus our proposed algorithm is not a corollary of the DS program outlines in ``\m {\ell_1}-MAGIC''.

@@

Since our setting is slightly different from ``\m {\ell_1}-MAGIC'', for completeness of exposition we write down derivation of the dual problem from the primal problem, as follows.
Recapitulate that, as we explained in the above, DS involves the calculation of \m {\ell_1}-1 norm.
This, for real vectors, can be transformed into a linear program (LP).
But in the complex case, that becomes a quadratic expression of the real and imaginary part of the vector, and is no longer equivalent to an LP.
Still, the comparison arising from primal-dual problem is not easily done in complex numbers, and we cast it into a real \m {\ell_1}-1 norm problem.
Afterwards we will further transform the SOCP to a primal-dual algorithm, which is a well-known technique for convex optimization problems.
The bound in the previous section is valid, since in the course of transformation, nothing is lost or weakened.

@@

\Result
{Definition}
{
For \m {x \in \MB {V} (M)}, we say \m {\MC {R} (x)} is the real representation of \m {x}, defined by
%
\Disp {
\NC \MC {R} (x) \in \NC \MB {V} (2M) \NR[+]
\NC \MC {R} (x) \DB {m} =
\NC \startcases
\MF {Re} (\MC {R} (x)\DB {m}), \quad \MC m =2m' \NR
\MF {Im} (\MC {R} (x)\DB {m}), \quad \MC m =2m'+1 \NR
\stopcases \NR[+]
\NC m' \NC =  1, \dots, M \NR
}
%
}

@@

\Result
{Definition}
{
For \m {A \in \MB {M}_{\MB {C}} (M_1, M_2)}, we say \m {\MC {R} (A)} is the real representation of \m {A}, defined by
%
\Disp {
\NC A \in \NC \MB {V}_{\MB {R}} (2M_1, 2M_2) \NR[+]
\NC A (m_1,m_2) =
\NC \startcases
\MF {Re} (A (m_1,m_2)), \quad \MC m_1 =2m_1'-1,\; m_2 =2m_2'-1  \NR
\MF {Im} (A (m_1,m_2)), \quad \MC m_1 =2m_1',\; m_2 =2m_2'-1  \NR
-\MF {Im} (A (m_1,m_2)), \quad \MC m_1 =2m_1'-1,\; m_2 =2m_2'  \NR
\MF {Re} (A (m_1,m_2)), \quad \MC m_1 =2m_1',\; m_2 =2m_2'  \NR
\stopcases \NR[+]
\NC m_1' \NC = 1, \dots, m_1 \NR[+]
\NC m_2' \NC = 1, \dots, m_2 \NR
}
%
}

@@

%
\Disp {
\NC \V {\T {y}}
\NC = \MC {R} (y)
\in \MB {V} (N_h) \NR[+]
\NC \V {\T {g}}
\NC = \MC {R} (g)
\in \MB {V} (N_h) \NR[+]
\NC \M {\T {P}}
\NC = \MC {R} (\M {P})
\in \MB {M}_{\MB {C}} (2 N_y^2, 2 N_h^2) \NR
}
%
such that
%
\Disp {
\NC \V {\T {y}} \NC = \M {\T {P}} \V {\T {g}} +\V {\T {z}}
}
%
where by construction
%
\Disp {
\NC \V {\T {z}}
\NC = \MC {R} (\V {z}) \in \MB {V} (N_y) \NR
}
%

Finally, introduce the following matrices to identify the components where we want to take \m {\ell_2}-norm, in the manner similar to an indicator function.

%
\Disp {
\NC \M {I}_{n_y}^{(y)} \in \NC \MB {M}_{\MB {R}} (2N_y^2, 2N_y^2) \NR[+]
\NC \M {I}_{n_y}^{(y)} (n_y')
\NC =
\startcases
1, \quad \MC n_y' =2n_y \NR[+]
1, \quad \MC n_y' =2n_y +1 \NR[+]
0, \quad \NC otherwise
\stopcases \NR[+]
\NC \M {I}_{n_h}^{(h)} \in \NC \MB {M}_{\MB {R}} (2N_h^2, 2N_h^2) \NR[+]
\NC \M {I}_{n_h}^{(h)} (n_h')
\NC =
\startcases
1, \quad \MC n_h' =2n_h \NR[+]
1, \quad \MC n_h' =2n_h +1 \NR[+]
0, \NC otherwise
\stopcases \NR[+]
\NC n_y \NC = 1, \dots, N_y \NR[+]
\NC n_h \NC = 1, \dots, N_h \NR
}
%

If we introduce vector \m {\V {m}} to denote the entrywise complex modulus, we see that Program () now take the form

\Result
{Program}
{
Given are \m {\T {\M {P}}, \T {\V {y}}, \gamma}.
Find \m {\T {\V {g}}} with
%
\Disp {
\NC \T {\V {g}}
\NC = \startcases
\NC \Min {\T {\V {g}}, \V {m}} \quad
\MC \IP { \V {1}, \V {m} } \NR
\NC \RM {subject} \; \RM {to} \quad
\MC \VNm { \M {I}_{n_h}^{(h)} \T {\V {g}} }_2
\leq \IP { \V {y}_{n_h}, \V {m} } \NR
\NC \MC \VNm { \M {I}_{n_y}^{(y)} \T {\M {P}}^\H \RB { \T {\M {P}} \T {\V {g}} -\T {\V {y}} } }_2
\leq \gamma \NR
\stopcases \NR
}
%
where \m {\V {1}} is the all-1 vector.
}

@@

It remains to convert primal-dual interior point algorithm to make the SOCP easier to calculate.
Of course it is not the only way to do this.
We mention, again, Boyd and Vandenberghe (2004), {\it Convex Optimization} chap.11 as a standard reference, and ``\m {\ell_1}-MAGIC'' (Cand\`es and J Romberg 2005) for discussion of application to DS.

To clarify notation and for complentess of exposition, we derive the dual problem here.
Start with the Lagrangian \m {\MC {L}}, where we note we have to introduce one auxiliary vector and one auxiliary scalar for each \m {\ell_2}-norm constraint.

%
\Disp {
\NC \NC \MC {L} (\V {m}, \T {\V {g}}, \V {\mu}^{(h)}, \V {\mu}^{(y)}, \lambda^{(h)}, \lambda^{(y)}) \NR[+]
\NC \NC = \IP {\V {1}, \V {m}}
+\sum_{n_h} \SB {\IP {\V {\mu}^{(h)}, \M {I}_{n_h}^{(h)} \T {\M {g}}} -\lambda^{(h)} \IP {\V {y}_{n_h}, \V {m}}} \NR[+]
\NC \quad \NC  +\sum_{n_y} \SB { \IP { \V {\mu}^{(h)}, \M {I}_{n_y}^{(y)} \T {\M {P}}^\H ( \T {\M {P}} \T {\V {g}} -\T {\V {y}} ) } -\lambda^{(h)} \gamma} \NR[+]
}
%

### 2019-03-05 ongoing/report/5_conclusion.tex
Reformatting source

\startsection [title={Conclusion}]

@@

Afterwards we transformed DS into an SOCP, which is quite different as in the original DS (where we have an LP instead).
Simulation is done, and DS's performance is compared to OMP.
{ \color{red} (To be done) }

@@

\startsection [title={References}]

References are sorted first with alphabetical order, then, in case for exactly the same author(s), with year.

\startenumerate

\item M R Akdeniz et.\ al.\ (2014), ``Millimeter Wave Channel Modeling and Cellular Capacity Evaluation'', \textit{IEEE Journal on Selected Areas in Communications}, Vol.\ 32, No.\ 6

\item A Alkhateeb, O E Ayach, G Leus, and R W Heath Jr (2014), ``Channel Estimation and Hybrid Precoding for Millimeter Wave Cellular Systems'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 8, No.\ 5.

\item A Alkhateeb, G Leus, and R W Heath Jr.\ (2015), ``Compressed Sensing Based Multi-User Millimeter Wave Systems: How Many Measurements are Needed?'' \textit{IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP)}

\item W U Bajwa, J Haupt, A M Sayeed, and R Nowak (2010), ``Compressed Channel Sensing: A New Approach to Estimating Sparse Multipath Channels'', Proceedings of the IEEE, Vol.\ 98, No.\ 6.

\item W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing'', 2008 42nd Annual Conference on Information Sciences and Systems.

\item R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', \textit{Constructive Approximation} \textbf{28}: 253–263

\item Zvika Ben-Haim, Y C Eldar, and M Elad (2010), ``Coherence-Based Performance Guarantees for Estimating a Sparse Vector Under Random Noise'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 58, No.\ 10.

\item S Boyd, L Vandenberghe (2004), \textit{Convex Optimization}. Cambridge U.\ Press.

\item E J Cand\`es, J Romberg, and T Tao (2006), ``Robust Uncertainty Principles: Exact Signal Reconstruction From Highly Incomplete Frequency Information'' \textit{IEEE Transactions on Information Theory}, Vol.52, No.2.

\item E J Cand\`es and J Romberg (2005), ``\(\ell_1\)-MAGIC: Recovery of Sparse Signals via Convex Programming'', Retrieved from \url{https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf}.

\item E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \textit{IEEE Transactions on Information Theory}, Vol.51, No.12.

\item E J Cand\`es and T Tao (2006), ``Near-Optimal Signal Recovery From Random Projections: Universal Encoding Strategies?'' \textit{IEEE Transactions on Information Theory}, Vol.52, No.12.

\item E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.35, No.6.

\item T T Cai and L Wang (2011), ``Orthogonal Matching Pursuit for Sparse Signal Recovery With Noise'', \textit{IEEE Transactions on Information Theory}, Vol.\ 57, No.\ 7.

\item T T Cai, L Wang, and G Xu (2010), ``Stable Recovery of Sparse Signals and an Oracle Inequality'', \textit{IEEE Transactions on Information Theory}, Vol.\ 56, No.\ 7.

\item M P Friedlander and M A Saunders (2007), ``Discussion: The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.\ 35, No.\ 6.

\item Z Gao, L Dai, Z Wang, and S Chen (2015). ``Spatially Common Sparsity Based Adaptive Channel Estimation and Feedback for FDD Massive MIMO'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 63, No.\ 23.

\item A Goldsmith, S A Jafar, N Jindal, and S Vishwanath (2003), ``Capacity Limits of MIMO Channels'', \textit{IEEE Journal on Selected Areas in Communications}, Vol.\ 21, No.\ 5.

\item R W Heath Jr, N González-Prelcic, S Rangan, W Roh, and A M Sayeed (2016), ``An Overview of Signal Processing Techniques for Millimeter Wave MIMO Systems'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 10, No.\ 3.

\item J Lee, G-T Gil, and Y H Lee (2016), ``Channel Estimation via Orthogonal Matching Pursuit for Hybrid MIMO Systems in Millimeter Wave Communications'', \textit{IEEE Transactions on Communications}, Vol.\ 64, No.\ 6.

\item H Li, Q Gao, R Chen, R Tamrakar, S Sun, and W Chen, ``Codebook Design for Massive MIMO Systems in LTE'', \textit{2016 IEEE 83rd Vehicular Technology Conference (VTC Spring)}.

\item X Rao and V K N Lau (2014), ``Distributed Compressive CSIT Estimation and Feedback for FDD Multi-User Massive MIMO Systems'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 62, No.\ 12.

\item J A Tropp and A C Gilbert (2007a), ``Signal Recovery from Random Measurements via Orthogonal Matching Pursuit: The Gaussian Case'', Caltech, ACM Tech.\ Rep. Retrieved from: \url{www.acm.caltech.edu/~jtropp/reports/TG07-Signal-RecoveryTR.pdf}

\item J A Tropp and A C Gilbert (2007b), ``Signal Recovery From Random Measurements via Orthogonal Matching Pursuit'', \textit{IEEE Transactions on Information Theory}, Vol.\ 53, No.\ 12.

\startenumerate

>>>>

\startchapter [title={Conclusion}]

@@

Afterwards we transformed DS into an SOCP, which is quite different as in the original DS (where we have an LP instead).
Simulation is done, and DS's performance is compared to OMP.
\color[red]{(To be done)}

@@
